### 2014-08-07 Studies/2012_Chicago/Report/Chicago_Fire.tex
Chicago: minor update to report

Based on the information collected, several engineering approximations were made. The actual ignition time is unknown.

The following subsections will describe the inputs that were used to construct the simulation, including any approximations or assumptions that were made.

>>>>

The focus of the analysis of the model results is on the interior second floor conditions prior to and after the interior door failure. Based on the goals of the analysis and the information collected, several engineering approximations were made. For example, it is known that the fire showed signs of being under-ventilated when firefighters arrived~\cite{NIOSH:Bowyer}, however the exact ignition time, fire growth rate, and energy release of the fire were not known. The ignition time and growth rate were estimated to balance computational runtime while adhering to documented observations. The energy release of the fire was estimated using documentation of the potential fuel load within the structure. Though there may exist differences with respect to the actual values compared to though used in the model, the inputs were determined to best model this fire scenario. The following subsections will describe the inputs that were used to construct the simulation, including any approximations or assumptions that were made.
